The Neuro Bureau ADHD-200 Preprocessed Repository

### 2016-05-14 Bellec_ADHD200_2016.tex
Fixed point 7 of reviewer 2 (inproper legend for Figure 1).

In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention-deficit/hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}. The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}. The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals (585 typically-developing controls (TDC), 362 ADHD, 26 unknown) \cite{Milham2012}. Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels on test data for which diagnostic information was withheld. The competition data was distributed in a raw form and, before any analysis could begin, the images had to be preprocessed to make them comparable across individuals and reduce noise. These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to high performance computing resources. Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.

@@

\begin{figure}[!t]
\begin{center}
  \includegraphics[width=0.6\linewidth]{fig_burner}
  \caption{Grey matter density maps generated by the Burner pipeline. An example of an individual map is presented, along with the average and standard deviation maps for all subjects in the test subsample of ADHD-200 Preprocessed. }
  \label{fig:burner}
\end{center}
\end{figure}

>>>>

In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers, from a variety of analytical backgrounds, to identify biomarkers of attention-deficit/hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}. The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}. The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals (585 typically-developing controls (TDC), 362 ADHD, 26 unknown) \cite{Milham2012}. Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels on test data for which diagnostic information was withheld. The competition data was distributed in a raw form and, before any analysis could begin, the images had to be preprocessed to make them comparable across individuals and reduce noise. These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to high performance computing resources. Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.

@@

\begin{figure}[!t]
\begin{center}
  \includegraphics[width=0.6\linewidth]{fig_burner}
  \caption{Average and standard deviation of the grey matter density maps generated by the Burner pipeline, for all subjects in the test subsample of ADHD-200 Preprocessed. }
  \label{fig:burner}
\end{center}
\end{figure}
